Generating Simulated Data

### 2021-03-23 docs/SimData.Rmd

@@

# write the csvs
o.name <- here("simulated-data/msinput/hydra/")
write_csv(foodweb, paste0(o.name,"foodweb_NOBA.csv"))
write_csv(specieslist, paste0(o.name,"speciesList_NOBA.csv"))
write_csv(lenwtpar, paste0(o.name,"lengthweight_species_NOBA.csv"))
write.csv(intakespp, paste0(o.name,"intake_species_NOBA.csv"))
write.csv(sizepref, paste0(o.name,"mortality_M2sizePreference_NOBA.csv"))
write.table(t(singletons), paste0(o.name,"singletons_NOBA.csv"), sep=",",  col.names=FALSE)
write.csv(M1, paste0(o.name,"mortality_M1_NOBA.csv"))

@@

>>>>

# placeholders for unused covariates dimenstioned to the number of simulated years
dummycovar <- data.frame(dummy1 = rep(1, NOBAom_ms$runpar$nyears))

@@

# write the csvs
o.name <- here("simulated-data/msinput/hydra/")
write_csv(foodweb, paste0(o.name,"foodweb_NOBA.csv"))
write_csv(specieslist, paste0(o.name,"speciesList_NOBA.csv"))
write_csv(lenwtpar, paste0(o.name,"lengthweight_species_NOBA.csv"))
write.csv(intakespp, paste0(o.name,"intake_species_NOBA.csv"))
write.csv(sizepref, paste0(o.name,"mortality_M2sizePreference_NOBA.csv"))
write.table(t(singletons), paste0(o.name,"singletons_NOBA.csv"), sep=",",  col.names=FALSE)
write.csv(M1, paste0(o.name,"mortality_M1_NOBA.csv"))
write_csv(dummycovar, paste0(o.name,"recruitment_covariates_NOBA.csv"))
write_csv(dummycovar, paste0(o.name,"maturity_covariates_NOBA.csv"))
write_csv(dummycovar, paste0(o.name,"growth_covariates_NOBA.csv"))

@@

Output temperature data from surveys using "Temp" variable in .nc file and the `atlantisom::load_nc_physics` function. A survey (timestep, polygons, possibly observation error) can then be applied to this output.

We can get surface and bottom temp from atlatis using the layers from each polygon, with layer 0 (?) being the surface and the maximum layer in the polygon being the bottom. 
```{r}

# taken from existing load_nc

file.nc <- file.path(d.name, "outputnordic_runresults_01.nc")

  # Load ATLANTIS output!
  at_out <- RNetCDF::open.nc(con = file.nc)

  # Get info from netcdf file! (Filestructure and all variable names)
  var_names_ncdf <- sapply(seq_len(RNetCDF::file.inq.nc(at_out)$nvars - 1),
    function(x) RNetCDF::var.inq.nc(at_out, x)$name)
  n_timesteps <- RNetCDF::dim.inq.nc(at_out, 0)$length
  n_boxes     <- RNetCDF::dim.inq.nc(at_out, 1)$length
  n_layers    <- RNetCDF::dim.inq.nc(at_out, 2)$length

RNetCDF::close.nc(at_out)

#'@physic_variables A character value spefifying which variables
#'   should be loaded. Only one variable can be loaded at a time.
#'   Currently, only the following variables are allowed:
#'   "salt", "NO3", "NH3", "Temp", "Oxygen", "Si", "Det_Si", "DON",
#'    "Chl_a", "Denitrifiction", "Nitrification".

truetemp <- atlantisom::load_nc_physics(dir = d.name,
                  file_nc = "outputnordic_runresults_01.nc",
                  physic_variables = "Temp",
                  aggregate_layers = FALSE,
                  bboxes = atlantisom::get_boundary(NOBAom_ms$boxpars))
  #if(verbose) message("Temperature read in.")

truetempagg <- atlantisom::load_nc_physics(dir = d.name,
                  file_nc = "outputnordic_runresults_01.nc",
                  physic_variables = "Temp",
                  aggregate_layers = TRUE,
                  bboxes = atlantisom::get_boundary(NOBAom_ms$boxpars))
